---
title: "NMR multiplet simulator"
author: "Paolo Pirovano"
date: "6 March 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=10, fig.height=2) 
load("figures.Rdata")
source("scripts/plotters.R")
library(ggplot2)
```

## What is this app about?

- A Shiny app to simulate the fine structure in NMR spectra
- This has got nothing to do with statistics or data science
- I had it half-done already from a personal project

## So, um, what's an NMR?

- No need to worry, just take it as a squiggly line generator
- https://en.wikipedia.org/wiki/Nuclear_magnetic_resonance_spectroscopy
- https://en.wikipedia.org/wiki/J-coupling


Why would I want it?

- Chemistry/physics homework maybe?

## How do I use it?

Input your list of nuclides in the table

      - I = nuclear magnetic moment (0.5, 1, 1.5, ...)
      
      - J = Coupling constant (whatever you want)
      
      - n = number of equivalent nuclides (positive integer)



Enjoy! (r code for the figures was sourced in header)

``` {r}
plotSpec(figures[[1]])
```

## Line broadening

We get finite linewidth with a gaussian convolution (?) of the spectral lines.
You can select the broadening with the slider.

``` {r, echo = FALSE}
plotSpec(figures[[1]])
plotSpecLb(figures[[2]])
```
